Compute last modified dates

### 2022-06-07 src/link_files.Rmd
Added deploy-now.md

```{r}
old_path <- "c:/Users/simons/Dropbox/professional/fun stuff/update-website/"
old_pattern <- "html$"
new_path <- "../text/"
new_pattern <- "md$"
subdir_list=c("99", paste0("0", 0:9), 10:22)
for (yr in subdir_list) {
  print(yr)
  file_path <- paste0(new_path, yr)
  file_path %>%
    list.files(pattern="md$") -> new_list
  new_list %>%
    str_remove_all("-") %>%
    str_remove_all(fixed(".md")) %>%
    str_remove_all(fixed(".Rmd")) %>%
    tolower %>%
    data.frame %>%
    set_names("key") %>%
    mutate(y=yr) %>%
    bind_cols(data.frame(md=new_list)) -> new_names
  file_path <- paste0(old_path, yr)
  file_path %>%
    list.files(pattern="html$") -> old_list
  old_list %>%
    tolower %>%
    str_remove_all(fixed(".html")) %>%
    data.frame %>%
    set_names("key") %>%
    mutate(y=yr) %>%
    bind_cols(data.frame(html=old_list)) %>%
    full_join(new_names, by=c("y", "key")) %>%
    arrange(key) %>%
    filter(is.na(md)|is.na(html)) %>%
    select(-key) %>%
    mutate(md=ifelse(is.na(md), "", md)) %>%
    mutate(html=ifelse(is.na(html), "", html)) %>%
    print
}
```

>>>>

```{r}
old_path <- "c:/Users/simons/Dropbox/professional/fun stuff/update-website/"
old_pattern <- "html$"
new_path <- "../text/"
new_pattern <- "md$"
subdir_list=c("99", paste0("0", 0:9), 10:22)
combined_list <- NULL
missing_links <- NULL
for (yr in subdir_list) {
  print(yr)
  file_path <- paste0(new_path, yr)
  file_path %>%
    list.files(pattern="md$") -> new_list
  repeat_names <- intersect(combined_list, new_list)
  if (length(repeat_names) > 0) print(repeat_names)
  new_list %>%
    str_remove_all("-") %>%
    str_remove_all(fixed(".md")) %>%
    str_remove_all(fixed(".Rmd")) %>%
    tolower %>%
    data.frame %>%
    set_names("key") %>%
    mutate(y=yr) %>%
    bind_cols(data.frame(md=new_list)) -> new_names
  file_path <- paste0(old_path, yr)
  file_path %>%
    list.files(pattern="html$") -> old_list
  old_list %>%
    tolower %>%
    str_remove_all(fixed(".html")) %>%
    data.frame %>%
    set_names("key") %>%
    mutate(y=yr) %>%
    bind_cols(data.frame(html=old_list)) %>%
    full_join(new_names, by=c("y", "key")) %>%
    arrange(key) %>%
    filter(is.na(md)|is.na(html)) %>%
    select(-key) %>%
    mutate(md=ifelse(is.na(md), "", md)) %>%
    mutate(html=ifelse(is.na(html), "", html)) %>%
    bind_rows(missing_links) -> missing_links
}
missing_links
```

Next step, search for 
+ [sim1]: http://www.pmean.com/??/...
+ <p>This page has moved to <a href="http://new.pmean.com/.../">a new website</a>.</p>
